Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180822.tex
tex/older_tex/ removed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}

\begin{figure*}
%%trim=l b r t
  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

We assemble our dataset in a relatively straightforwad manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

We then obtain optical, near-infrared and mid-infrared photometry for the
spectral dataset.

The optical data comes from the 
Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.

The near-infrared data comes from the Wide Field Camera (WFCAM) on 
the United Kingdom Infra-Red Telescope

\subsection{Very high redshift quasars}
In Table~\ref{tab:THE_TABLE} we give the discovery reference for the
VH$z$Qs noting that some objects were discovered independently and
contemporaneously.  The redshifts for the VH$z$Qs generally come from
the measurement of broad UV/optical emission lines. Where 
there are far infra-red emission lines e.g. \cii~158 micron, we report 
these, but at the level of our current analysis broadline redshifts are
sufficient.

@@

Table~\ref{tab:THE_TABLE} gives the salient details for the objects
used in this study. We use all the $z\geq5.00$ quasars that
have been discovered and spectroscopically confirmed as of the time of
writing (2018 June). We report near-infrared ($yYJHK$-bands)
and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
$M_{1450}$

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey   & \# VH$z$Qs & Notes  \\
\hline  
  ATLAS      &    4    &  \\
  CFHQS     &  20    &  \\
  DELS        &    2    &  \\
  ELAIS       &    1    &  \\
  FIRST       &    1    &  \\
  HSC         &    8    &  \\
  IMS          &   1     &  \\
  MMT        &  12    &  \\
  NDWFS    &  1      &  \\
  PSO          &    84  & \\
  RD           &  1       & \\
  SDSS        & 156       & \\
  SOUV       & 20       & \\
  SDWISE    & 27& \\
  SHELLQs  & 55 & \\
  ULAS       & 10& \\
  VDES       & 11& \\
  VIK          & 9 &\\
  VIMOS     & 1& \\
\hline  \hline
\end{tabular}
\caption{ATLAS \citet{Shanks2015}; }
      \label{tab:surveys}
\end{table}

@@

    We query and return the mean PSF magnitudes from the $grizy$ filters
    ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
    sample. Details of our SQL and links to the main tables are given
    in~\ref{sec:PS1_SQL}.

    \subsubsection{DECam}

@@

@@

\subsubsection{UKIDSS LAS} 
Use:\\
%lasDetection \\
dr10plus\\
lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned. Of which...

\subsubsection{VISTA VHS} 
Use:\\
%lasDetection \\
VH5DR5 \\
sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned.  Of which...

@@

%    \begin{equation}
%      \label{equ:simple_prob}
%      dP = n \, dV.
%    \end{equation}

%    \begin{eqnarray}
%      \xi_{LS}(s) &=& 1 + \left(\frac{N_{rd}}{N} \right)^{2} \frac{DD(s)}{RR(s)} -
%      2   \left( \frac{N_{rd}}{N} \right) \frac{DR(s)}{RR(s)} \\
%      &\equiv&  \frac{DD(s)-2DR(s)+RR(s)}{RR(s)},
%      \label{lseq}
%    \end{eqnarray}

%% http://www-astro.physics.ox.ac.uk/~kmb/latex_colour.html
%{\color{red} ...bit of LaTeX text...}
%an example of making an equation the colour DarkSeaGreen (rather a sophisticated shade, I think) one types the following:
%\begin{equation}
%{\color{DarkSeaGreen} x = \log_{10} (\nu/\rm MHz) }
%\end{equation}

%\subsection{Dust Overview}
%http://arxiv.org/pdf/1605.06671.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
 Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus convallis ac. Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam eu blandit. Donec in lacinia libero.

\subsection{Detection Rates}
%\begin{table}
 % \begin{center}
  %  \setlength{\tabcolsep}{4pt}
   % \begin{tabular}{lrrr}
     % \hline       \hline
    %  Sample Description  & Number in sample & North & South   \\
     % \hline
     % \hline \hline
%      \label{tab:The_Numbers}
 %   \end{tabular}
  %  \caption{}
  %\end{center}
%\end{table}

@@

\subsection{Very High-$z$ Quasars Detected in WISE}
\citet{Blain2013} 
Cras in laoreet mauris. Vivamus nec nulla a dui commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida sagittis quis in sem. Phasellus quis risus bibendum eros luctus auctor.

@@

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
the blue or red end respectively. Hmmm....}
   \label{fig:filters}
 \end{figure*}

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
}
   \label{fig:filters}
 \end{figure*}

%\subsection{Number Density of High-$z$ Sources}

\subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
From a study of 69 {\it Herschel}-detected broad-line active galactic
nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
for the $z>6$ measured from the e.g. \mgii line, are generally
correct, then the galaxy total stellar mass for the $z>6$ objects
should be...

\citet{YangG2018} calculate the long-term SMBH accretion rate as a
function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
Our BHAR(M⋆,z) is constrained by high-quality survey data
(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
function and the X-ray luminosity function.  This BHAR/SFR dependence
on $M_{\star}$ does not support the scenario that SMBH and galaxy
growth are in lockstep.

@@

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:filters}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:filters}
\end{figure*}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

\section{Data}
We assemble our dataset in a relatively straightforwad manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

We then obtain optical, near-infrared and mid-infrared photometry for the
spectral dataset. The optical data comes from the 
Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.

The near-infrared data comes from two primary sources. First, the Wide
Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
\citep[Visible and Infrared Survey Telescope for
Astronomy;][]{Emerson2006, Dalton2006}.

Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
of the filters in question.

\subsection{Very high redshift quasars}
In Table~\ref{tab:THE_TABLE} we present our dataset. 
We have obtained a list of 424 spectroscopically confirmed 
quasars with redshifts $z\geq5.00$.

In Table~\ref{tab:THE_TABLE}  we give the discovery reference for the
VH$z$Qs noting that some objects were discovered independently and
contemporaneously.  The redshifts for the VH$z$Qs generally come from
the measurement of broad UV/optical emission lines. Where 
there are far infra-red emission lines e.g. \cii~158 micron, we report 
these, but at the level of our current analysis broadline redshifts are
sufficient.

@@

Table~\ref{tab:THE_TABLE} gives the salient details for the objects
used in this study. We use all the $z\geq5.00$ quasars that
have been discovered and spectroscopically confirmed as of the time of
writing (2018 June). We report near-infrared ($yYJHK$-bands)
and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
$M_{1450}$.

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey   & \# VH$z$Qs & Notes/Survey reference  \\
\hline  
  ATLAS      &     4    &  \citet{Shanks2015} \\
  CFHQS     &   20    &  \citet{Willott2007} \\
  DELS        &     2    &  \citet{Dey2018} \\
  ELAIS       &     1    &  \citet{Vaisanen2000} \\
  FIRST       &     1    &  \citet{Becker1995} \\
%  HSC         &     8    &  \\
  IMS          &     1     &  \citet{Kim2015} \\
  MMT        &   12    &  \citet{McGreer2013} \\
  NDWFS    &     1     &  \citet{JD1999} \\
  PSO          &   84    &   \citet{Kaiser2002, Kaiser2010} \\
  RD           &     1       &  \cite{Mahabal2005} \\
  SDSS        & 156       & \citet{EDR} \\
  SDUV       &   20       & \citet{Yang2017} \\
  SDWISE    &   27    &     \citet{Wang2016} \\
  SHELLQs  &  $^{a}$63   &  \citet{Matsuoka2016}\\  %% includes 8 objects from the first HSC paper..
  ULAS       &   10   & \citet{Lawrence2007} \\
  VDES       &   11   &  \citet{Reed2017} \\
  VIK          &     9   &  \citet{Edge2013} \\
  VIMOS     &     1   &  \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference. 
$^{a}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018}  
designation.
}
      \label{tab:surveys}
\end{table}

@@

    We query and return the mean PSF magnitudes from the $grizy$ filters
    ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
    sample. Details of our SQL and links to the main tables are given
    in Appendix~\ref{sec:PS1_SQL}.

    \subsubsection{DECam} 
    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
    is a wide-field imager with a 2.2 degree diameter field of view 
    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
    at the Cerro Tololo International Observatory. We use data 
    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}.

@@

\subsubsection{UKIDSS LAS} 
In a bit more detail, use:\\
dr10plus\\
lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned. Of which...

\subsubsection{VISTA VHS} 
In a bit more detail, use:\\
VH5DR5 \\
sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
424 results returned.  Of which...

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Having collated the sample of 424 VH$z$Qs, and obtained their optical,
near- and mid-infrared photometry we report here the various
photometric properites of the quasars.

First, we will concentrate on detection rate in the infrared, go on to
report on the color-redshift and color-color properties of our sample
and then report on how the current sample populates the
luminosity-redshift $Lz$-plane.

    \subsection{Detection Rates in the optical}

    \subsection{Detection Rates in the NIR}
    Table~\ref{tab:nir_detection} gives the detection rates for the 
    VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
    The first thing to note is that the coverage of the NIR surveys 
    for example from the UKIDSS LAS and VISTA VHS, does
    not overlap the full area for where the VH$z$Qs are detected.

    \begin{table}
      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($YJHK/K_{s}$   &  394  ( ) \\
        $Y$-band    &    ( ) \\
        $J$-band    &    ( ) \\
        $H$-band    &    ( ) \\
        $K$ or $Ks$-band    &    ( ) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

    \subsection{Detection Rates in the MIR}
    Unlike the NIR coverage, the WISE
    satellite and mission performed an all-sky survey, so the location of
    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
    ALLWISE survey depends heavily on sky location, with locations near
    the Ecliptic Poles having the highest number of exposures.

    Before reporting on the detection rates, we investigate this
    effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
    versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
    coverage depth, in each corresponding band. In the two shorter bands
    W1/2 we see the clear and expected trend for brighter objects to have
    larger SNR, and also for the higher signal to noise for objects with
    more exposures at a given magnitude. The behaviour for the W3/4 bands
    is different, with two populations clearly evident in W3 and although
    a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
    no obvious R.A./Declination dependence seen, this behaviour is
    explained by the fact that there are non-detectiopns in W3/4 for
    objects (with high W1/2 SNR) that are reported in the ALLWISE
    catalogue.

    For the 278 VH$z$Q with coverage detections, the mean number of
    exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
    minimum number of exposures 17 and 12, and the maximum number or
    exposures being 114 (for both bands).  For the W3/4 filters, the
    corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
    5.8 and 6.8 and 69 (for both bands). These values are direclty from
    the {\tt w$x$cov} enteries in the 
    \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.

    \begin{figure}
      %% trim=l b r t
      \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
      \centering
      \vspace{-14pt}
      \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
        colour coded by w$x$cov the mean coverage depth, in each corresponding band.
  }
  \label{fig:WISEmag_vs_coverage}
\end{figure}

    Table~\ref{tab:mir_detection} gives the detection rates for the
    VH$z$Qs in the MIR WISE W1-4 bands. 
    \begin{table}
      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        W1 SNR $> 2.0$   &  275  (64.9) \\
        W2 SNR $> 2.0$   &   255 (60.1) \\
        W1 \&\& W2 SNR $> 2.0$  &  \\
        W3 SNR $> 2.0$   &  99    (23.3) \\
        W4 SNR $> 2.0$   &  29    (6.8) \\
        Any W1/2/3/4 SNR $>2.0$ & \\
        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
        \hline  \hline
      \end{tabular}
      \caption{ATLAS \citet{Shanks2015}; }
      \label{tab:mir_detection}
    \end{table}

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE signal-to-noise measures for the four bands, as well
    as for (W1-W2) colour.  The points are colour coded by redshift.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}

@@

    \subsection{Very High-$z$ Quasars in WISE}
     \citet{Blain2013} 
     Cras in laoreet mauris. Vivamus nec nulla a dui commodo
     adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
     ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
     et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
     sagittis quis in sem. Phasellus quis risus bibendum eros luctus
     auctor.

@@

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
the blue or red end respectively. Hmmm....}
   \label{fig:SpecType_vs_NIRcolors}
 \end{figure*}

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
}
   \label{fig:SpecType_vs_W1W2_W2W3colors}
 \end{figure*}

@@

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:Lz}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:RestWavelength_SEDs}
\end{figure*}

@@

This project used data obtained with the Dark Energy Camera (DECam)
and the NOAO Data Lab, The Data Lab is operated by the National
Optical Astronomy Observatory, the national center for ground-based
nighttime astronomy in the United States operated by the Association
of Universities for Research in Astronomy (AURA) under cooperative
agreement with the National Science Foundation.
